---
title: "Update_07_21.Rmd"
author: "Jia Zhao"
date: "7/21/2020"
output: 
  html_notebook:
    toc: yes
---
## Load sacCer1.2bit in R and convert to a csv for better analysis in Python
```{r}
library(rtracklayer)
#Convert 2bit sequence data to a data frame and export as csv
S288c20031001 <- import.2bit('sacCer1.2bit')
S288cSeqDF <- data.frame(S288c20031001)
write.csv(S288cSeqDF, file = "S288c_genome_seq.csv")
```

## Python:  find all consensus and 1-bp-off motifs in *S. cerevisiae*. 
Export a 'Motif.csv' including information **"chromosome", "motif", "start" and "end"** position. Pay attention to **element[2] = index + occurrence * len(motif)** in find_motif(motif,seq) function, which is different from my previous code. It's a bug I fixed yesterday to get the original start position of a motif after I remove the first detected motif.
```{python}
# Find a motif in a seq: Fuzzy search consensus/1 bp off motif 
consensus_motif= "CACGTG"
data=[]

# Find a motif 
def find_motif(motif,seq):
    occurrence=0
    start_position=[]
    while motif in seq:
        mylist = []
        element[1] = motif
        index = seq.find(motif) # Find the first motif
        seq = seq[:index] + seq[index+len(motif):] # Remove the first detected motif
        start_position.append(index + occurrence * len(motif)) # Get the original index
        element[2] = index + occurrence * len(motif)
        element[3] = element[2] + len(motif)
        mylist = mylist + element # mylist includes one piece of infomation for one motif
        occurrence = occurrence + 1
        data.append(mylist)
    
# Fuzzy search of 1 base pair off motif
my_list = ["C", "A", "T", "G"]
def find_1_bp_off_motif():
    b=[]
    for i in range(6):
        for j in range(4):
            a= ""
            if my_list[j] == consensus_motif[i]:
                continue
            else:
                a = consensus_motif[:i] + str(my_list[j]) + consensus_motif[i+1:]
                b.append(a)
    for i in range(len(b)):
        find_motif(b[i], seq)       

# S288c_genome 20031001 saccer1 (DNAStringSet)converted to csv in R
# Report all of the consensus and 1-bp off motifs in the genome
# Information include "chromosome", "motif", "start position", "end position"

element=["chromosome", "motif", "start position", "end position"]
seq = ""
with open("S288c_genome_seq.csv", 'r') as f:
    for line in f:
        if "chr" in line:
            line = line.split(sep = ",")
            element[0] = line[0]
            seq = line[1]
            find_motif(consensus_motif, seq)
            find_1_bp_off_motif()
        else:
            continue

import csv
with open('Motif.csv', 'w', newline = '') as h:
    writer = csv.writer(h)
    writer.writerows(data)        


```

## Import "Motif.csv" in R

```{r }
S288cMotif <- read.csv("Motif.csv", header = FALSE)
colnames(S288cMotif) <- c("chromosome", "motif", "start", "end")
View(S288cMotif)
```


